---
title: "dinar"
author: "Markus Skyttner"
date: "`r Sys.Date()`"
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


[![Build Status](https://travis-ci.org/DINA-Web/dinar.svg)](https://travis-ci.org/ropensci/rfishbase)

Welcome to `dinar`. This package provides an R interface to the DINA-Web APIs.

```{r include=FALSE}
knitr::opts_chunk$set(warning=FALSE, comment=NA)
```

## Installation

```{r message=FALSE, warning=FALSE, results="hide", eval=FALSE}
#install.packages("dinar", 
#  repos = c("http://packages.ropensci.org", "http://cran.rstudio.com"),  type="source")
```


```{r message=FALSE, warning=FALSE, results="hide"}
library(dinar)
```

## Getting started


[DINA-Web](http://dina-project.net) is a Free and Open-Source digital Natural History Collections management system for the Web. It provides REST APIs providing access to collections data and the `dinar` R-package provides an R client or interface to these APIs.

### Getting data

Here is an example of getting "institution" data from the API and printing the response:

```{r}
library(dinar)

res <- dw_get(dw_api(path = "institution"))
print(res)

```

Here are the collections and an example of printing the names of those.

```{r}
collections <- dw_get(dw_api(path = "collection"))
collections$content$collectionName
```
