---
title: "Importing Redlist data"
author: "Markus Skyttner"
date: "05/14/2015"
output: html_document
---

## Downloading 2015 redlist status data from web service

To get redlist status information related to Dyntaxa species we use Python in `redlist.py` to retrieve XML data from a SOAP web service, keeping these specific considerations in mind:

0. use https://taxonattribute.artdatabankensoa.se/TaxonAttributeService.svc
0. login with credentials from a local configuration file to retrieve the info using a set of criteria
0. criteria need to be combined with AND (see redlist.py code)
0. criteria require magic numbers (undocumented, but verbally communicated from Björn), ie one needs to use the following settings:
  * FactorIds = 743
  * IndividualCategoryIds = 0
  * PeriodIds = 4
  * TaxonIds = 100145 (optional, if left out, all species will be fetched)

Running `redlist.py` we get a 70 MB large `redlist-info.xml` XML-file that contains slightly cryptic information in XML which needs to be processed further and injected into the database. 

## Uploading processed data to db

For this purpose we use `redlist.R` which performs a number of steps:

0. Removes namespace information from `redlist-info.xml` for performance reasons and calls `redlist-xml2csv.py` which quickly parses out the relevant XML paths and converts data to CSV, making the following considerations:
  * The abbreviated (2 or 3 chars long string) redlist status is in the XML tag `FieldValue4` (src: Björn)
  * The dyntaxa identifier is in the XML tag `TaxonId`
1. Uses an inline reference data lookup table to translate the redlist status abbreviations to understandable text strings in Swedish and English
0. Reads related data from the db from "The Naturalist" to determine latinname, vernacular name, linkage to identifiers used there (`taxon_uuid` visavi `dyntaxa_id`)
0. Assembles a dataset and uploads the dataset to "The Naturalist"

## How to run this migration

Firstly, on a networked machine, preferably linux as `sed` is used in a system call, make sure you have  `Python` and `R` installed and that you have these files:

* redlist.py (to download XML from web service)
* redlist-xml2csv.py (to convert XML to CSV)
* redlist.R (to process and upload redlist data to db)
* redlist-credentials.cfg (holding your login credentials both for the web service and database)

Then issue the following CLI commands from your working dir to run the download and upload steps:
```console
# set permissions
chmod 600 redlist-credentials.cfg
chmod +x redlist.R

# dl data fr ws
python redlist.py

# ul data to db
./redlist.R
```

### Installing required deps / libs for R and Python

The .py files uses `suds` which is a library for making SOAP web service calls. You can find installation instructions on the web, for example see: https://stackoverflow.com/questions/2057380/installing-suds-in-python-2-6-4

The .R file uses `dplyr` and `plyr` for data manipulation and `RMySQL` for db access. To install R with those packages, try:
  
```console
# install Debian/Ubuntu OS deps - ie R and a mysql client library
sudo apt-get install r-base r-base-dev libmysqlclient-dev

# install dplyr and plyr packages into R system
sudo su - -c "R -e \"install.packages(pkgs = c('dplyr', 'plyr', 'RMySQL'), repos='http://cran.rstudio.com/')\""
```

# Sources

## Configurations with credentials data
One configuration file is used, `redlist-credentials.cfg`. This is a text file with sections and name value pairs, that looks like this:
```{r, echo=FALSE, message=FALSE, results='asis'}
code <- readLines("redlist-credentials.cfg")
code <- gsub("password=.*", "password=dummy", code)
code <- gsub("pass=.*", "pass=dummy", code)
code <- paste(collapse = "\n", code)
cat("```console\n", code, "\n```")
```

## redlist.py
Downloads 70 MB of XML from SOAP ws, stores it in a file.
```{r, echo=FALSE, message=FALSE, results='asis'}
code <- paste(collapse = "\n", readLines("redlist.py"))
cat("```console\n", code, "\n```")
```

## redlist-xml2csv.py
Quickly parses XML data, picking out relevant fields and converting to CSV.
```{r, echo=FALSE, message=FALSE, results='asis'}
code <- paste(collapse = "\n", readLines("redlist-xml2csv.py"))
cat("```console\n", code, "\n```")
```

## redlist.R
Cleans, decorates, processes data and uploads it into "redlist_2015" db table
```{r, echo=FALSE, message=FALSE, results='asis'}
code <- paste(collapse = "\n", readLines("redlist.R"))
cat("```console\n", code, "\n```")
```
